A Systematic Review of the Use of the ESM Methodology in Education

### 2020-08-05 paper_draft.Rmd
update
update 1

This study  is a systematic review of studies in education that used the experience sampling method to collect data.

>>>>

This is a test to ensure the proper pushing....
CHecking push and pull
This study  is a systematic review of studies in education that used the experience sampling method to collect data.
